### 2019-05-07 tii/tex/evaluation.tex
Reduce the number of ref to 30

\subsubsection{Terasort}
We also evaluate Terasort\cite{terasort} --- a recognized shuffle intensive benchmark for distributed system analysis. 
Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
It further proves the effectiveness of SCache's optimization.

>>>>

\subsubsection{Terasort}
We also evaluate Terasort\footnote{http://sortbenchmark.org/YahooHadoop.pdf} --- a recognized shuffle intensive benchmark for distributed system analysis. 
Terasort consists of two consecutive shuffles. 
The first shuffle reads the input data and uses a hash partition function for re-partitioning. 
As shown in Figure \ref{fig:terasort}, Spark with SCache runs 2 $\times$ faster during the reduce stage of the first shuffle, which is consistent with the results in Section \ref{simpledag}. 
It further proves the effectiveness of SCache's optimization.

### 2019-05-07 tii/tex/impl.tex
Reduce the number of ref to 30

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{black} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture like GFS \cite{gfs} for the shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{black} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{black} the original scheduler in framework}.

@@

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 380 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez \cite{tez}, are also low.
}

\subsection{Discussion of Fault Tolerance}\label{fault}
Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
We plan to implement SCache master with Apache ZooKeeper \cite{zookeeper} to provide constantly service. 
If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
A possible way to handle this failure is selecting some backup nodes to store replications. 
But the replications can introduce a significant network overhead \cite{availability}.  
Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
Meanwhile, SCache can still provide shuffle optimization during the recovery.

>>>>

\subsection{System Overview}\label{arch}
SCache consists of three components: a distributed shuffle data management system, a DAG co-scheduler, and a %{\color{red}daemon inside Spark.}
{\color{black} worker daemon. As a plug-in system, SCache needs to rely on a DAG framework.} As shown in Figure \ref{fig:architecture}, SCache employs the legacy master-slaves architecture for the shuffle data management system. 
The master node of SCache coordinates the shuffle blocks globally with application context. The worker node reserves memory to store blocks.
The coordination provides two guarantees: (a) data is stored in memory before tasks start and (b) data is scheduled on-off memory with all-or-nothing and context-aware constraints. 
The daemon bridges the communication between %{\color{red}Spark}
{\color{black} DAG framework} and SCache. The co-scheduler is dedicated to pre-schedule reduce tasks with DAG information and enforce the scheduling results to %{\color{red}Spark scheduler}
 {\color{black} the original scheduler in framework}.

@@

To prove the cross-framework capability of SCache, we adapt SCache on Hadoop MapReduce and Spark respectively. In Hadoop MapReduce, we modify codes in ResourceManager, MapTask, and ReduceTask to call SCache APIs through RPC. It takes about 380 lines of code. In Spark, we mainly modify DAGScheduler and the corresponding data fetcher. 
It only takes about 500 lines of code. Such hundreds of lines of code modification are very small compared to the hundreds of thousands of lines of code in DAG framework. We believe that the costs of enabling SCache on other DAG computing frameworks, such as Tez, are also low.
}

\subsection{Discussion of Fault Tolerance}\label{fault}
Due to the characteristic of shuffle data (e.g., short-lived, write-once, read-once), we believe fault tolerance is not a crucial goal of SCache at present. 
We plan to implement SCache master with Apache ZooKeeper \footnote{https://zookeeper.apache.org/} to provide constantly service. 
If a failure happens inside the SCache worker, SCache daemon can block the shuffle write/read operations until the worker process restarts without violating the correctness of the DAG computing.
A possible way to handle this failure is selecting some backup nodes to store replications. 
% But the replications can introduce a significant network overhead \cite{availability}.  
Currently, we leave the sever faults (e.g., the failure of a node) to the DAG frameworks. 
We believe it is a more promising way because most DAG frameworks have more advanced fast recovery schemes on the application layer, such as paralleled recovery of Spark. 
Meanwhile, SCache can still provide shuffle optimization during the recovery.

### 2019-05-07 tii/tex/intro.tex
Reduce the number of ref to 30

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark \cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{black}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad} and Tez \cite{tez}, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
{\color{black}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, duan2016selection, tang2018intermediate, sync, tachyon, heintz2016end, zhang2015prism, cheng2017improving, chen2017heterogeneous, wasi2017comprehensive, chen2013tiled}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{black}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

@@

{\color{black}
We have implemented SCache on both Apache Spark \cite{apachespark} and Hadoop MapReduce. 
% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

>>>>

\section{Introduction}\label{sec:introduction}
\IEEEPARstart{W}{e} are in an era of data explosion --- 2.5 quintillion bytes of data are created every day according to IBM's report\footnote{http://www-01.ibm.com/software/data/bigdata/}.
{\color{black}
In \textit{industry 4.0}, an increasing number of IoT sensors are embedded in the industrial production line \cite{lade2017manufacturing}.
During the manufacturing process, the information about the assembly lines, stations, and machines is continuously generated and collected.
Using distributed computing frameworks to analyze industrial big-data is an inevitable trend \cite{lee2014service}.
% \cite{ibmreport}.
% These data come from a variety of industry, e.g., records in industrial production, digital pictures and videos in social networks, and sensors used for Internet of Things (IoT).
% These data come from a variety of industries, e.g., e-commerce, telecommunications, media, retail customers and social networks.
% \cite{chen2012interactive}.
% Whether the data is generated from industrial production or social networks, the analysis methods are almost MapReduce-related\cite{lv2017next}.
% Nowadays, the real challenge of big data is not how to collect it, but how to manage it logically and efficiently\cite{lv2017next}.
Several sophisticated frameworks are used in industrial big-data analysis such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\footnote{https://spark.apache.org/}, and Storm\footnote{http://storm.apache.com/}.
% The analysis method for these industrial big data mainly relies on MapReduce-liked frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Spark\cite{spark}, and Storm\footnote{http://storm.apache.com/}.
% Recent years have witnessed the widespread use of sophisticated frameworks, such as Hadoop MapReduce\footnote{http://hadoop.apache.com/}, Dryad \cite{dryad}, Spark \cite{spark}, and Apache Tez \cite{tez}.
Industrial big-data is more structured, correlated, and ready for analytics than traditional big-data, because industrial big-data is generated by automated equipment \cite{basanta2018efficient, lv2017next}.
}

{\color{black}
According to a cross-industry study \cite{chen2012interactive}, both industrial and traditional big-data share a characteristic during analytical processing --- a small fraction of the daily workload uses well over 90\% of the cluster’s resources, and these workloads often contain a huge shuffle size. 
According to another MapReduce trace analysis from Facebook, the shuffle phase accounts for $33\%$ of the job completion time on average, and up to $70\%$ in shuffle-heavy jobs \cite{managing}.
The shuffle phase is crucial and heavily affecting the end-to-end application performance.
Most of the popular frameworks define jobs as directed acyclic graphs (DAGs), such as map-reduce pipeline in Hadoop MapReduce, lineage of resilient distributed datasets (RDDs) in Spark, vertices and edges in Dryad \cite{dryad}, and Tez\footnote{https://tez.apache.org/}, etc.
Despite the differences among data-intensive frameworks, the shuffle phase is always essential as communication between successive computation stages.
}

\begin{figure}
	\centering
	\includegraphics
		[width=1\linewidth]
		{fig/workflow}
	\caption{Workflow Comparison between Legacy DAG Computing Frameworks and Frameworks with SCache}
	\label{fig:workflow}
\end{figure}
{\color{black}
Although continuous efforts of performance optimization have been made among a variety of computing frameworks\cite{chen2017parallel, sync, tachyon, heintz2016end, cheng2017improving, wasi2017comprehensive}, the shuffle phase is often poorly optimized in practice.
In particular, we observe that one major deficiency lies in the coupled scheduling among different system resources.
}
%In the current practice, the shuffle phase is often split into two parts --- \textit{shuffle read} and \textit{shuffle write}. 
As Figure \ref{fig:workflow} shows, the \textit{shuffle write} is responsible for writing intermediate results to disk, which is attached to the tasks in ancestor stages (i.e., map task).  
And the \textit{shuffle read} fetches intermediate results from remote disks through network, which is commonly integrated as part of the tasks in descendant stages (i.e., reduce task). 
Once scheduled, a fixed bundle of resources (i.e., CPU, memory, disk, and network) named \textit{slot} is assigned to a task, and the resources are released only after the task finishes.
{\color{black}
Such task aggregation together with the coupled scheduling effectively simplifies task management.
}
However, since a cluster has a limited number of slots, attaching the I/O intensive shuffle phase to the CPU/memory intensive computation phase results in a poor multiplexing between computational and I/O resources.
%The map task in Figure \ref{fig:workflow} well explains such deficiency: the I/O resource allocated to the stage is always idle during the computation time, and the computation/memory resource is totally wasted during the shuffle write attached to it, and vice versa.

@@

{\color{black}
We have implemented SCache on both Spark and Hadoop MapReduce. 
% We have also designed a performance model called FRQ model to analyze the shuffle optimization of SCache and predict the execution time of each phase of a computing job. 
The performance of SCache is evaluated with both simulations and testbed experiments on a 50-node Amazon EC2 cluster on both Apache Spark and Apache Hadoop. On Apache Spark, we conduct a basic test - \textit{GroupByTest}. We also evaluate the system with Terasort\footnote{https://github.com/ehiggs/spark-terasort} benchmark and standard workloads like TPC-DS\footnote{http://www.tpc.org/tpcds/} for multi-tenant modeling. On Apache Hadoop, we focus on Terasort benchmark. In a nutshell, SCache can eliminate explicit shuffle time by at most $89\%$ in varied applications. More impressively, SCache reduces $~40\%$ of overall completion time of TPC-DS queries on average on Apache Spark. On Apache Hadoop, SCache optimizes end-to-end Terasort completion time by $15\%$.
}

### 2019-05-07 tii/tex/motivation.tex
Reduce the number of ref to 30

\textbf{Overview of shuffle process}. 
Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
The total number of buckets equals the number of reduce tasks in the successive step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
\textbf{Impact of shuffle process}. Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
Can we mitigate or even remove the overhead of shuffle? 
To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
Unfortunately this defect exists not only in Spark \cite{apachespark} but also Hadoop MapReduce and Apache Tez \cite{tez}. 
A finer granularity resource allocation scheme should be provided to reduce these delays.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU utilization and I/O throughput of a node during a Spark single shuffle application}
	\label{fig:util}
	\vspace{-1em}
\end{figure}

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
Compared to input dataset, the size of shuffle data is relatively small. 
For example, the shuffle size of Spark Terasort is less than $25\%$ of input data. 
The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
On the other hand, memory based distributed storage systems have been proposed \cite{memcached, tachyon, ramcloud} to move data back to memory, 
but most of the DAG frameworks still store shuffle data on disks (e.g., Spark \cite{apachespark}, Hadoop MapReduce, Dryad \cite{dryad}, etc).
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

>>>>

% \textbf{Overview of shuffle process}

\subsubsection{Overview of shuffle process}
Each map task partitions the result data (key, value pair) into several buckets according to the partition function (e.g., hash). 
The total number of buckets equals the number of reduce tasks in the successive step.
% shuffle data is produced by \textit{data partition}. For \textit{data partition}, 
The shuffle process can be further split into two parts: \textit{shuffle write} and \textit{shuffle read}. 
Shuffle write starts at the end of a map task and writes the partitioned map output data to local persistent storage. 
Shuffle read starts at the beginning of a reduce task and fetches the partitioned data from remote as its input.

%In short, shuffle is loosely coupled with application context and it's I/O intensive.
% \textbf{Impact of shuffle process}

\subsubsection{Impact of shuffle process}
Shuffle is I/O intensive, which might introduce a significant latency to the application. 
Reports show that $60\%$ of MapReduce jobs at Yahoo! and $20\%$ at Facebook are shuffle-heavy workloads \cite{shufflewatcher}. 
For those shuffle-heavy jobs, the shuffle latency may even dominate Job Completion Time (JCT).
For instance, a MapReduce trace analysis from Facebook shows that shuffle accounts for $33\%$ JCT on average, up to $70\%$ in shuffle-heavy jobs \cite{managing}.
% Besides, the completion time of shuffle correlates with the performance of storage devices, network and even applications.
% This variation may bring a huge challenge for operators to find the correct configuration of the DAG framework.

\subsection{Observations} \label{observation}
% Of course, shuffle is unavoidable in a DAG computing process. 
Can we mitigate or even remove the overhead of shuffle? 
To find the answers, we ran some typical Spark applications on a 5-node \texttt{m4.xlarge} EC2 cluster and analyzed the design and implementation of shuffle in some DAG frameworks.
Here we present the hardware utilization trace of one node running Spark's \textit{GroupByTest} in Figure \ref{fig:util} as an example. 
This job has 2 rounds of tasks for each node.
The \textit{Map Execution} is marked from the launch time of the first map task to the execution end time of the last one. 
The \textit{Shuffle Write} is marked from the beginning of the first shuffle write in the map stage. 
The \textit{Shuffle Read and Reduce Execution} is marked from the launch time of the first reduce task.
% Figure \ref{fig:util} reveals the performance information of two stages that are connected by shuffle. By analyzing the trace with Spark source code \cite{sparksource}, we propose the following observations.
% \begin{figure*}
% 	\includegraphics[width=\textwidth]{fig/util}
% 	\caption{CPU utiliazation and I/O throughput of a node during a Spark single shuffle application}
% 	\label{fig:util}
% \end{figure*}
\subsubsection{Coarse Granularity Resource Allocation}
When a slot is assigned to a task, it will not be released until the task completes (i.e., the end of shuffle write in Figure \ref{fig:util}). 
On the reduce side, the network transfer of shuffle data introduces an explicit I/O delay during shuffle read (i.e., the beginning of shuffle read and execution in Figure \ref{fig:util}). 
Meanwhile, both shuffle write and shuffle read occupy the slot without significantly involving CPU as presented in Figure \ref{fig:util}. 
The current coarse slot-task mapping results in an imbalance between task's resource demand and slot allocation thus decreasing the resource utilization. 
Unfortunately this defect exists not only in Spark but also Hadoop MapReduce and Tez. 
A finer granularity resource allocation scheme should be provided to reduce these delays.

\subsubsection{Synchronized Shuffle Read}
Almost all reduce tasks start shuffle read simultaneously. 
The synchronized shuffle read requests cause a burst of network traffic. 
As shown in Figure \ref{fig:util}, 
the data transfer causes a high demand of network bandwidth, which may result in network congestion and further slow down the network transfer.
It also happens in other frameworks that follow Bulk Synchronous Parallel (BSP) paradigm, such as Hadoop MapReduce, Dryad \cite{dryad}, etc.
% The previous work \cite{coflow, managing} also proves that the network transfer can introduce significant overhead in DAG computing.
\begin{figure}
	\includegraphics[width=\linewidth]{fig/util}
	\caption{CPU Utilization and I/O Throughput of a Node During a Spark Single Shuffle Application}
	\label{fig:util}
	\vspace{-1em}
\end{figure}

\subsubsection{Inefficient Persistent Storage Operation}
At first, both shuffle write and read are tightly coupled with task execution, which results in a blocking I/O operation. 
This blocking I/O operation along with synchronized shuffle read may introduce significant latency, especially in an I/O performance bounded cluster.
Besides, the legacy of storing shuffle data on disk is inefficient in modern clusters with large memory. 
Compared to input dataset, the size of shuffle data is relatively small. 
For example, the shuffle size of Spark Terasort is less than $25\%$ of input data. 
The data reported in \cite{makingsense} also show that the amount of data shuffled is less than the input data by as much as $10\%-20\%$. 
On the other hand, memory based distributed storage systems have been proposed \cite{tachyon, ramcloud} to move data back to memory, 
but most of the DAG frameworks still store shuffle data on disks (e.g., Spark, Hadoop MapReduce, Dryad \cite{dryad}, etc).
We argue that the memory capacity is large enough to store the short-living shuffle data with cautious management.

### 2019-05-07 tii/tex/optimization.tex
Reduce the number of ref to 30

As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune, reining, gufler2012load}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle, predict}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

@@

For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
and applies the longest processing time rule (LPT) \cite{design} to achieve $4/3\text{-}approximation$ optimum. 
Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.

>>>>

As shown in Figure \ref{fig:sim}, the baseline (i.e., red dotted line) is the stage completion time with Spark FIFO scheduling algorithm. 
We then remove the shuffle read time of each task and run the simulation under three scheduling schemes: random mapping, Spark FIFO, and our heuristic MinHeap.
Random mapping works well when there is only one round of tasks, but the performance drops as the round number grows. 
This is because that data skew commonly exists in data-parallel computing \cite{skewtune}. 
Several heavy tasks may be assigned to the same node, thus slowing down the whole stage. 
In addition, randomly assigned tasks also ignore the data locality between shuffle map output and reduce input, which may introduce extra network traffic in cluster.

@@

For the most DAG applications with random large scale input, 
the $BlockSize_{ji}$ in a particular shuffle can be predicted accurately by liner regression model (i.e., equation \ref{linearregresion}) based on observation that the ratio of map output size and input size are invariant given the same job configuration \cite{guo2017ishuffle}: 
\begin{equation}
\label{linearregresion}
\begin{aligned}
	BlockSize_{ji} = a \times inputSize_j + b
\end{aligned}
\end{equation}
The $inputSize_j$ is the input size of $j$th map task. 
The $a$ and $b$ can be determined using the observed $inputSize_j$ and $BlockSize_{ji}$.

@@

For the pre-scheduling itself (i.e., the first $while$ in Algorithm \ref{hminheap}), the algorithm maintains a min-heap to simulate the load of each node 
and applies the longest processing time rule (LPT)\footnote{http://www.designofapproxalgs.com/} to achieve $4/3\text{-}approximation$ optimum. 
Since the sizes of tasks are considered while scheduling, Heuristic MinHeap can achieve a shorter makespan than Spark FIFO which is a $2\text{-}approximation$ optimum. 
Simulation of OpenCloud trace in Figure \ref{fig:sim} also shows that Heuristic MinHeap has a better improvement (average 5.7\%) than the Spark FIFO (average 2.7\%).
% After the scheduling, the completion time of reduce stage is close to the optimal. \textcolor{red}{may need to add math prove between this and optimal}.
After pre-scheduling, the task-node mapping will be adjusted according to the locality. 
The $SWAP\_TASKS$ will be triggered when the $host\_id$ of a task does not equal the $assigned\_id$.
% The closer $prob$ is to $1/m$, the more evenly this reduce partition is produced in cluster.
Based on the $prob$, the normalized probability $norm$ is calculated as a bound of performance degradation. 
% We set maximum $upper\_bound$ of performance degradation equals to 10\% that can be traded for locality (in extreme skew scenarios).
Inside the $SWAP\_TASKS$, tasks will be selected and swapped without exceeding the $upper\_bound$.
